Maximising the leverage of existing knowledge could reduce research waste in applied ecology and conservation

### 2019-11-25 Manuscript/MS.Rmd
update 25/11/2019

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
      tab1 [label = '@@1',color = blue]
      tab2 [label = '@@2',color = blue]
      tab3 [label = '@@3',color = blue]
      tab4 [label = '@@4',color = blue]
      tab5 [label = '@@5',color = red]
  node [shape = circle,
        fixedsize = true,
        width = 2, color=green] // sets as circles
    tab6 [label = '@@6']
    # several 'edge' statements
 tab1->tab2->tab3->tab4
 tab1->tab5
  tab2->tab5
   tab3->tab5
    tab4->tab5
    tab4->tab6 
    tab6->tab1 [style=dotted]
        tab6->tab2 [style=dotted]
        tab6->tab5 [style=dashed]

}
      [1]: 'Questions relevant to stakeholders'
      [2]: 'Appropriate design & methods'
      [3]: 'Accessible full publication'
      [4]: 'Unbiased reporting'
      [5]: 'Research waste'
      [6]: 'Evidence synthesis'
", height=1000)

@@

cum_df2<-cum_df[c(1,18,27),]
#png("TSA.png", width=850, height =400)
cum_df %>% 
  ggplot(aes(cum_sample,z.score, colour=as.factor(Year)))+
  scale_fill_npg()+
  labs(y="Cumulative z score", x="Cumulative sample size")+
  geom_point(size=6)+
  geom_line(colour="blue", linetype="dashed", size=1)+
  ylim(c(-20,20))+
  xlim(c(0,2000))+

>>>>

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
      tab1 [label = '@@1',color = blue]
      tab2 [label = '@@2',color = blue]
      tab3 [label = '@@3',color = blue]
      tab4 [label = '@@4',color = blue]
      tab6 [label = '@@6',color = blue]
      tab8 [label = '@@8',color = red]
      tab9 [label = '@@9',color = red]
      tab10[label = '@@10',color = red]
      tab11[label = '@@11',color = red]

  node [shape = circle,
        fixedsize = true,
        width = 2, color=blue] // sets as circles
    tab7 [label = '@@7']

    node [shape = circle,
        fixedsize = true,
        width = 2, color=red] // sets as circles
    tab5 [label = '@@5']

    # several 'edge' statements
 tab1->tab2->tab3->tab4->tab6->tab7 [color=blue]
 tab1->tab8 [color=red,style=dashed]
  tab2->tab9 [color=red,style=dashed]
   tab3->tab10 [color=red,style=dashed]
    tab4->tab11 [color=red,style=dashed]
    tab8->tab5[color=red,style=dashed]
    tab9->tab5[color=red,style=dashed]
    tab10->tab5[color=red,style=dashed]
    tab11->tab5[color=red,style=dashed]
    tab6->tab1 [style=dashed]
        tab6->tab2 [style=dashed]
    tab6->tab5 [color=red, style=dashed]

 }
      [1]: 'Questions relevant to stakeholders'
      [2]: 'Appropriate design & methods'
      [3]: 'Accessible full publication'
      [4]: 'Unbiased reporting'
      [5]: 'Wasteful research'
      [6]: 'Evidence synthesis'
      [7]: 'Utilisable research' 
      [8]: 'Previous knowledge not accounted for'
      [9]: 'Poor design; \\nquestionable research practices'
      [10]: 'Publications not available to practitioners \\n& decision makers'
      [11]: 'Lack of transparency'
  ", height=1000)

@@

cum_df2<-cum_df[c(1,18,27),]
#png("TSA.png", width=850, height =400)
cum_df %>% 
  ggplot(aes(cum_sample,z.score))+
  scale_fill_npg()+
  labs(y="Cumulative z score", x="Cumulative sample size")+
  geom_point(size=3, colour="blue")+
  geom_line(colour="blue", linetype="dashed", size=1)+
  ylim(c(-20,20))+
  xlim(c(0,2000))+
